### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@41bffe33263a66da386f48c0bf4dbb2d9a7ad9dd 🚀

A diagram showing the relation between these packages is shown in
fig.~\ref{fig:software}. \texttt{MetacommunityDynamics.jl} is built on
\texttt{DynamicGrids.jl}, a library for high-performance gridded
simulations in the \texttt{Julia} language, and Dispersal.jl (Maino
\emph{et al.} 2021), and extension of \texttt{DynamicGrids.jl}
specifically for modeling organism dispersal. It also contains
integrations with \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.}
2019) to generate metawebs, or can use empirical networks from Mangal.jl
(Banville \emph{et al.} 2021). It implements the general framework for
community dynamics proposed by (\textbf{Velland2010ConSyn?}), where all
community processes can divided into four categories: selection,
dispersal, drift, and speciation.

@@

>>>>

A diagram showing the relation between these packages is shown in
fig.~\ref{fig:software}. \texttt{MetacommunityDynamics.jl} is built on
\texttt{DynamicGrids.jl}, a library for high-performance gridded
simulations in the \texttt{Julia} language, and Dispersal.jl (Maino
\emph{et al.} 2021), and extension of \texttt{DynamicGrids.jl}
specifically for modeling organism dispersal. It also contains
integrations with \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.}
2019) to generate metawebs, or can use empirical networks from Mangal.jl
(Banville \emph{et al.} 2021). It implements the general framework for
community dynamics proposed by Vellend (2010), where all community
processes can divided into four categories: selection, dispersal, drift,
and speciation.

@@

\leavevmode\hypertarget{ref-Vellend2010ConSyn}{}%
Vellend, M. (2010). Conceptual Synthesis in Community Ecology. \emph{The
Quarterly Review of Biology}, 85, 183--206.
